### 2020-09-28 README.Rmd
monetdblite -> duckdb (#10)
* monetdblite -> duckdb
* Fix connection pane to work with duckdb
* Code NAs correctly

Co-authored-by: Noam Ross <ross@ecohealthalliance.org>

```{r message = FALSE, warning = FALSE, error = FALSE, include = FALSE}
options(width = 120)
knitr::opts_chunk$set(cache = TRUE)
citesdb::cites_disconnect()
MonetDBLite::monetdblite_shutdown()
```

>>>>

```{r message = FALSE, warning = FALSE, error = FALSE, include = FALSE}
options(width = 120)
knitr::opts_chunk$set(cache = TRUE)
citesdb::cites_disconnect()
duckdb::duckdb_shutdown()
```
